---
title: "eds221-task-wild"
format: html
editor: visual
execute: 
  warning: false
---
```{r}
library(tidyverse)
library(janitor)
library(here)
```
```{r}

mack_verts <- read_csv(here("data", "AS00601.csv")) %>% clean_names()

```
store the fifth value in column "Weight" as mc_wt_5

```{r}
mc_wt_5 <- mack_verts$weight[5]
```

store 8th-20th value in the "LENGTH1" column as mc_length_8_20. check by looking at your data frame to confirm 

```{r}
i <- seq(8,20)
mc_length_8_20 <- mack_verts$length1[i]
```

store everything in colmumn SAMPLEDATE as a vector called mc_dates 

```{r}
mc_dates <- mack_verts$sampledate 
```
Create a subset that only contains observations for Pacific Giant Salamanders (species Dicamptodon tenebrosus, stored in species as DITE). Store the subset as mc_salamanders. Hint: see dplyr::filter()!

```{r}
mc_salamanders <- mack_verts %>% dplyr::filter(species == "DITE")
```

Create a scatterplot of length1 (snout-vent length in millimeters) versus weight (grams) for all salamanders in the subset you created above, mc_salamanders. Update axis labels, title, subtitle, and add a caption with the data source. Customize point color and size, possibly opacity, and theme.

```{r}
mc_salamanders %>% ggplot(aes(x= length1, y= weight)) + geom_point() + labs(title = "snout-vent length (mm) vs weight (g)") + xlab("length (mm)") + ylab("weight (g)")

ggsave(filename = "salamander_size.png", path = here("figs") )
```
Similar to above, make a subset called mc_trout that only contains observations for cutthroat trout (species “ONCL”)

```{r}
mc_trout <- mack_verts %>% dplyr::filter(species == "ONCL")
```

Create a scatterplot of length1 by weight for all trout in the dataset

```{r}
mc_trout_graph <- mc_trout %>% 
  ggplot(
    aes(x=length1, y=weight, color=mc_trout$sitecode)) +
  geom_point() + 
  facet_wrap(facets = "reach") + labs(title = "trout length by weight") + 
 ylab("weight") + xlab("length")
mc_trout_graph
```

Customize so that the point color depends on reach
Customize your color scheme (e.g. scale_color_manual())
Facet your plot by creek reach (facet_wrap(~...))
Update graph axis labels and title
Export your graph as cutthroat_size.png to the figs folder

```{r}
ggsave(filename="trout_length_by_weight_at_different_sites.png", path=here("figs"))

```



